paper_pdf

### 2020-03-21 paper_pdf.Rmd

prepared_data <- read_csv("data/prepared_data.csv", 
    col_types = cols(CHILDPOVRATE15 = col_number(), 
        CONVSPTH09 = col_number(), FFRPTH09 = col_number(), 
        FSRPTH09 = col_number(), GROCPTH09 = col_number(), 
        LACCESS_CHILD10 = col_number(), LACCESS_POP10 = col_number(), 
        METRO13 = col_number(), MILK_PRICE10 = col_number(), 
        PCT_18YOUNGER10 = col_number(), PCT_FREE_LUNCH09 = col_number(), 
        PC_SNAPBEN10 = col_number(), PC_WIC_REDEMP08 = col_number(), 
        PERCHLDPOV10 = col_number(), PERPOV10 = col_number(), 
        RECFACPTH09 = col_number(), SPECSPTH09 = col_number(), 
        SUPERCPTH09 = col_number(), VEG_ACRESPTH07 = col_number()))
food = read.csv("data/q1_and_q2.csv")
census <- read_csv("data/census.csv")
data <- sqldf::sqldf("SELECT * FROM prepared_data 
              JOIN census
              USING(FIPS)")
data <- data[-c(23,24)]

@@

@@

@@

We are also interested in another potential dependent variable: Count of children eligible for the free lunch program per hundred thousand. This is calculated by the authors by first finding out the total student population by multiplying the proportion of population aged under 18 years old with the population of the county (available through census data via the Food Environment Atlas) in 2018. Next, the number of students are multiplied by the Percent Eligibility for the Free Lunch Program to find the Count of children eligible for the Free Lunch Program. The final step is to divide this figure by the county population and multiply by 100,000 to get the Count of Children eligible for the Free Lunch Program per thousand.  One key assumption and thus future model limitation here is that in the absence of better data, we assume that the population under 18 is equal to the population of students of school going age.

@@

## Model Fitting: Poisson regression 
Now we are interested in seeing the relationship with the same independent variables but with the dependent variable of Count Eligi

>>>>

prepared_data <- read_csv("~/data/prepared_data.csv", 
    col_types = cols(CHILDPOVRATE15 = col_number(), 
        CONVSPTH09 = col_number(), FFRPTH09 = col_number(), 
        FSRPTH09 = col_number(), GROCPTH09 = col_number(), 
        LACCESS_CHILD10 = col_number(), LACCESS_POP10 = col_number(), 
        METRO13 = col_number(), MILK_PRICE10 = col_number(), 
        PCT_18YOUNGER10 = col_number(), PCT_FREE_LUNCH09 = col_number(), 
        PC_SNAPBEN10 = col_number(), PC_WIC_REDEMP08 = col_number(), 
        PERCHLDPOV10 = col_number(), PERPOV10 = col_number(), 
        RECFACPTH09 = col_number(), SPECSPTH09 = col_number(), 
        SUPERCPTH09 = col_number(), VEG_ACRESPTH07 = col_number()))
food = read.csv("~/data/q1_and_q2.csv")
census <- read_csv("~/data/census.csv")
data <- sqldf::sqldf("SELECT * FROM prepared_data 
              JOIN census
              USING(FIPS)")
data <- data[-c(23,24)]

@@

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} cccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & Estimate & Std. Error & t value & Pr(\textgreater \textbar t\textbar ) & robust.se \\ 
\hline \\[-1.8ex] 
(Intercept) & $30.238$ & $0.195$ & $155.211$ & $0$ & $0.226$ \\ 
GROCPTH09 & $$-$1.748$ & $0.348$ & $$-$5.021$ & $0$ & $0.449$ \\ 
SUPERCPTH09 & $22.895$ & $3.077$ & $7.440$ & $0$ & $2.885$ \\ 
CONVSPTH09 & $1.586$ & $0.204$ & $7.767$ & $0$ & $0.278$ \\ 
SPECSPTH09 & $$-$6.068$ & $0.829$ & $$-$7.322$ & $0$ & $0.744$ \\ 
WICSPTH08 & $0.932$ & $0.310$ & $3.006$ & $0.003$ & $0.492$ \\ 
FFRPTH09 & $$-$2.203$ & $0.220$ & $$-$10.034$ & $0$ & $0.272$ \\ 
FMRKTPTH09 & $$-$2.013$ & $0.898$ & $$-$2.243$ & $0.025$ & $1.045$ \\ 
RECFACPTH09 & $$-$9.349$ & $0.830$ & $$-$11.261$ & $0$ & $1.047$ \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

@@

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} cccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & Estimate & Std. Error & t value & Pr(\textgreater \textbar t\textbar ) & robust.se \\ 
\hline \\[-1.8ex] 
(Intercept) & $32.009$ & $0.239$ & $134.110$ & $0$ & $0.266$ \\ 
GROCPTH14 & $$-$4.417$ & $0.431$ & $$-$10.242$ & $0$ & $0.554$ \\ 
SUPERCPTH14 & $23.340$ & $3.261$ & $7.157$ & $0$ & $3.366$ \\ 
CONVSPTH14 & $1.718$ & $0.241$ & $7.124$ & $0$ & $0.340$ \\ 
SPECSPTH14 & $$-$6.487$ & $1.009$ & $$-$6.427$ & $0$ & $1.211$ \\ 
WICSPTH12 & $3.247$ & $0.442$ & $7.344$ & $0$ & $0.541$ \\ 
FFRPTH14 & $$-$2.297$ & $0.254$ & $$-$9.039$ & $0$ & $0.282$ \\ 
FMRKTPTH16 & $$-$2.484$ & $0.754$ & $$-$3.294$ & $0.001$ & $0.744$ \\ 
RECFACPTH14 & $$-$11.157$ & $1.069$ & $$-$10.433$ & $0$ & $1.189$ \\ 
FOOD\_TAX14 & $0.446$ & $0.036$ & $12.307$ & $0$ & $0.036$ \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

@@

We are also interested in another potential dependent variable: Count of children eligible for the free lunch program per hundred thousand. This is calculated by the authors by first finding out the total student population by multiplying the proportion of population aged under 18 years old with the population of the county (estimated using census methods) in 2018. Next, the number of students are multiplied by the Percent Eligibility for the Free Lunch Program to find the Count of children eligible for the Free Lunch Program. The final step is to divide this figure by the county population to get the Count of Children eligible for the Free Lunch Program per thousand.  One key assumption and thus future model limitation here is that in the absence of better data, we assume that the population under 18 is equal to the population of students of school going age.

@@
